Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-30 manuscript.Rmd
Table 1

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    imp1:imp16, # rapport during the interaction
    strait1:strait26, # perceivers' self-reported personality traits
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    InsecAtt:SIAPSc, # composite variables
    InformantTot, # number of informants for targets
    Extr:Trust, # composite variables for personality traits
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

@@

## Descriptive statistics
```{r, include = FALSE}
# descriptives
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)

@@

map2_dfr(item_list, variable_names, ~ 
           get_reliability(df = df_desc, 
                           items = .x, 
                           var_names = .y)
         )
```

per_open, per_cons, per_extra, per_agre, per_neur,
per_intel, per_trust,
tar_open, tar_cons, tar_extra, tar_agre, tar_neur,
tar_intel, tar_trust,
judg_open, judg_cons, judg_extra, judg_agre, judg_neur,
judg_intel, judg_trust

@@

```{r}
table1
```

>>>>

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    imp1:imp16, # rapport during the interaction
    strait1:strait26, # perceivers' self-reported personality traits
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    InsecAtt:SIAPSc, # composite variables
    InformantTot, # number of informants for targets
    Extr:Trust, # composite variables for personality traits of perceivers
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

@@

## Descriptive statistics
```{r, include = FALSE}
# descriptives
vars_desc <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, Open, Consc, Extr, Agree, Neurot, Intell, Trust
  ) %>% 
  names()

tab_desc <-  get_descriptives(df_desc[vars_desc])

@@

int_cons <- 
map2_dfr(item_list, variable_names, ~ 
           get_reliability(df = df_desc, 
                           items = .x, 
                           var_names = .y)
         )

# table 1
table1 <- bind_cols(tab_desc, int_cons) %>% 
  select(Variables = vars, N_Valid:Max, Alpha:Omega)
```

@@

```{r}
kable_style(table1, 
            title = "<center><b>Table 1: Descriptive Statistics and Internal Consistency</center></b>")
```
